curacao_threeplayers_rest_monster

### 2020-09-29 inst/curacao1962_threeplayers_rest_monster.Rmd
verification; reveals a flaw

```{r}
H <- hyper2(pnames=c(players,"white","draw","rest"))
for(i in seq_len(nrow(a))){
  white_player <- a[i,1]
  black_player <- a[i,2]

@@

  if(result == "1-0"){   # white win
    if(white_player_rested){
      H[c(white_player,"white","rest"                         )] %<>% inc
      H[c(white_player,"white","rest",black_player,drawmonster)] %<>% dec
    } else if(black_player_rested){
      H[c(white_player,"white"                                )] %<>% inc
      H[c(white_player,"white","rest",black_player,drawmonster)] %<>% dec
    } else { # neither player rested
      H[c(white_player,"white"                                )] %<>% inc
      H[c(white_player,"white",       black_player,drawmonster)] %<>% dec
    }
  } else if(result == "0-1"){  # black win
    if(white_player_rested){
      H[c(                            black_player            )] %<>% inc
      H[c(white_player,"white","rest",black_player,drawmonster)] %<>% dec
    } else if(black_player_rested){
      H[c(                     "rest",black_player            )] %<>% inc
      H[c(white_player,"white","rest",black_player,drawmonster)] %<>% dec
    } else { # neither player rested
      H[c(                            black_player            )] %<>% inc
      H[c(white_player,"white",       black_player,drawmonster)] %<>% dec
    }
  } else if(result == "1/2-1/2"){ # draw
      H[c(                                         drawmonster)] %<>% inc
      H[c(white_player,"white","rest",black_player,drawmonster)] %<>% dec
  } else { # not a white win or a black win or a draw
    stop("this cannot happen")
  }
}
H
(mH <- maxp(H))
pie(mH)
summary(H)
```

>>>>

```{r}
H <- hyper2(pnames=c(players,"white","draw","rest"))
prob <- function(...){stop("must be a white win or a black win or a draw")}
for(i in seq_len(nrow(a))){
  white_player <- a[i,1]
  black_player <- a[i,2]

@@

  if(result == "1-0"){   # white win
    if(white_player_rested){
      H[c(white_player,"white","rest"                         )] %<>% inc
      H[c(white_player,"white","rest",black_player,drawmonster)] %<>% dec
    } else if(black_player_rested){
      H[c(white_player,"white"                                )] %<>% inc
      H[c(white_player,"white","rest",black_player,drawmonster)] %<>% dec
    } else { # neither player rested
      H[c(white_player,"white"                                )] %<>% inc
      H[c(white_player,"white"       ,black_player,drawmonster)] %<>% dec
    }
  } else if(result == "0-1"){  # black win
    if(white_player_rested){
      H[c(                            black_player            )] %<>% inc
      H[c(white_player,"white","rest",black_player,drawmonster)] %<>% dec
    } else if(black_player_rested){
      H[c(                     "rest",black_player            )] %<>% inc
      H[c(white_player,"white","rest",black_player,drawmonster)] %<>% dec
    } else { # neither player rested
      H[c(                            black_player            )] %<>% inc
      H[c(white_player,"white",       black_player,drawmonster)] %<>% dec
    }
  } else if(result == "1/2-1/2"){ # draw
      H[c(                                         drawmonster)] %<>% inc
      H[c(white_player,"white"       ,black_player,drawmonster)] %<>% dec
  } else { # not a white win or a black win or a draw
    prob()
  }
}
H
(mH <- maxp(H))
pie(mH)
summary(H)
```

```{r,label=verify}
I <- hyper2(pnames=c(players,"white","draw","rest"))
for(i in seq_len(nrow(a))){
  white_player <- a[i,1]
  black_player <- a[i,2]

  if(white_player_rested){  
    if(       result == "1-0"){ 
      I[c(white_player,             "white","rest"            )] %<>% inc
    } else if(result == "0-1"){ 
      I[c(             black_player                           )] %<>% inc
    } else if(result == "1/2-1/2"){                         
      I[c(                                         drawmonster)] %<>% inc
    } else { prob() }
      I[c(white_player,black_player,"white","rest",drawmonster)] %<>% dec
  } else if(black_player_rested){
    if(       result == "1-0"){ 
      I[c(white_player,             "white"                   )] %<>% inc
    } else if(result == "0-1"){ 
      I[c(             black_player,        "rest"            )] %<>% inc
    } else if(result == "1/2-1/2"){                         
      I[c(                                         drawmonster)] %<>% inc
    } else { prob() }
      I[c(white_player,black_player,"white","rest",drawmonster)] %<>% dec
  } else { # neither player rested
    if(       result == "1-0"){ 
      I[c(white_player,             "white"                   )] %<>% inc
    } else if(result == "0-1"){ 
      I[c(             black_player                           )] %<>% inc
    } else if(result == "1/2-1/2"){                         
      I[c(                                         drawmonster)] %<>% inc
    } else { prob() }
      I[c(white_player,black_player,"white",       drawmonster)] %<>% dec
  }
}

I

summary(I)
maxp(I)
I==H
I + (-1)*H
```
